Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-04-26 GECCO/volunteer-clouds-gecco16.tex
First final version submitted to Sheridan
@mariosky, I could do it, no problem finally :-)

\documentclass{sig-alternate}

@@

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
% \author{Juan-J.~Merelo, Dept. of Computer Architecture and Technology
%   and CITIC, University of Granada, Granada, Spain \\
% Mario Garc\'ia-Valdez, Dept. of Graduate Studies, Instituto
% Tecnológico de Tijuana, Tijuana, M\'exico\\
% Pedro A. Castillo, Dept. of Computer Architecture and Technology, University of Granada, Granada, Spain\\
% Pablo Garc\'ia-S\'anchez, Dept. of Computer Architecture and Technology, University of Granada, Granada, Spain\\
% Paloma de las Cuevas, Dept. of Computer Architecture and Technology,
% University of Granada, Granada, Spain\\

% \thanks{Corresponding author: Juan-J.~Merelo (Email: jmerelo@ugr.es).}%
% }
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
}

@@

%---------------------------------------------------------------
% \section*{Acknowledgment}
% 
% This work has been supported in part by
% TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR), 
% SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico) and PYR-2014-17
% GENIL project (CEI-BIOTIC Granada). Additional support was recieved by
% Projects 5622.15-P (ITM) and  PROINNOVA 2015: 220590 (CONACYT).
% We would also like to thank the
% anonymous reviewers of previous versions of this paper who have really
% helped us to improve 
% this paper (and our work) with their suggestions. We are also grateful
% to Anna S\'aez de Tejada for her help with the data processing scripts.

>>>>

\documentclass{sig-alternate-05-2015}
\CopyrightYear{2016}
\setcopyright{rightsretained}
\conferenceinfo{GECCO'16 Companion}{July 20-24, 2016, Denver, CO, USA}
\isbn{978-1-4503-4323-7/16/07}
\doi{http://dx.doi.org/10.1145/2908961.2926999}

\clubpenalty=10000
\widowpenalty = 10000

@@

\numberofauthors{6}
\author{
\alignauthor
Juan-J.~Merelo, Pedro A. Castillo, Pablo Garc\'ia-S\'anchez, Paloma de las Cuevas\\
\affaddr{Dept. of Computer Architecture and Technology
  and CITIC, University of Granada, Granada, Spain} \\
\email{(jmerelo|pacv|pgarcia|palomacd)@ugr.es}
\alignauthor Nuria Rico\\
\affaddr{Dept. of Statistics, University of Granada, Granada, Spain}\\
\email{nrico@ugr.es}
\alignauthor
Mario Garc\'ia-Valdez,\affaddr{ Dept. of Graduate Studies, Instituto
Tecnol\'ogico de Tijuana, Tijuana, M\'exico}\\
}

@@

%---------------------------------------------------------------
\section*{Acknowledgment}

This work has been supported in part by
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR), 
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico) and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). Additional support was recieved by
Projects 5622.15-P (ITM) and  PROINNOVA 2015: 220590 (CONACYT).
